A Large-Scale Study of the Use of Eval in R

### 2020-08-25 inst/paper/main.tex
usage metrics (done)

In Figure~\ref{fig:ast-size}, we look at the the size of the AST, in number
of nodes, of the \c(expr) argument of \eval, after it is resolved.

\begin{figure}[htbp]
	\includegraphics[width=\columnwidth]{ast_sizes}
	\caption{Size of the \c{expr} argument of \eval in terms of AST nodes, for the \emph{core} dataset and the \emph{packages} dataset.} \label{fig:ast-size}
\end{figure}

Most of these expressions have very few nodes and about 50\% have only one. It is because \c{expr} is often reduced to just a value or a symbol.

\miss{This is on a random sample of 10000 unique rows of the summarized data set as ST size takes a lof of time to compute. To update when it finishes computing...}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{polymorphism}
    \caption{Degree of polymorphism of \c{expr} per call sites.} \label{fig:polymorphism}
\end{figure}

>>>>

To estimate the complexity of the code being evaluated,
Fig.~\ref{fig:ast-size} shows the distribution of the abstract syntax tree
size of the \c{expr} argument to \eval. The majority of inputs across core
and packages (\miss{XX}\%) is 1. That is to say, the code being evaluated
consists of a single variable name or constant. A function call needs at
least three nodes. Inputs smaller than \c{X} nodes account for 95\% of all
calls. Sizes are roughly similar between core and packages.

\begin{figure}[htbp]
\includegraphics[width=\columnwidth]{ast_sizes}
\caption{Input sizes} \label{fig:ast-size}
\end{figure}

\medskip\noindent\emph{Discussion:} Comparing the use of \eval in R and JavaScript is
instructive. The use of \eval is more widespread in data science code than
it was in JavaScript. Any run of an R program seems to trigger \eval, more
over package programmers use \eval liberally. On the other hand, the authors
of Kaggle packages do not use the feature at all.  This point to a
bifurcated user community, experts who write package know how to use \eval
while end-users do not. An alternative explanation is that end-users do not
need \eval for simple data analysis tasks. This bifurcation was not observed
in the JavaScript community, but this may have changed with the advent of
Node.js ecosystem.  The distribution of input sizes is similar to that found
in JavaScript, the majority of inputs being rather small.

@@

\begin{figure}[!h]
    \includegraphics[width=\columnwidth]{polymorphism}
    \caption{Degree of polymorphism of \c{expr} per call sites.} \label{fig:polymorphism}
\end{figure}
